The Effect of a Second AIDS Defining Illness on Survival in the MACS

### 2015-05-10 paper.Rmd
Fix intervals

tbl.pre <- data %>%
    transmute(site=CENTER,
              race=race,
              age.ge.40=ifelse(age.at.aids >= 40,
                               "age >= 40", "age < 40"),
              aids.year=cut(year(aids.date), c(1984, 1988, 1992, 1995), 
                                 include.lowest=TRUE),
              cd4.base=cut(cd4, c(0, 50, 200, Inf), include.lowest=TRUE),
              initial.aids=frst.aids.diag,
              second.aids=sec.aids.diag,
              depressed=ifelse(depression, "depressed", "not depressed"),
              drug.user=ifelse(drug.use, "Drug User", "Not a Drug User"),
              site=CENTER,
              died=year(death.date) < 2100,
              survival.time=difftime(death.date, aids.date, 
                                     units="weeks") / 52.25 * 12,
              survival.time=as.numeric(survival.time),
              survival.time=ifelse(died, survival.time, NA),
              survival.time.2=difftime(death.date, sec.aids.date,
                                       units="weeks") / 52.25 * 12,
              survival.time.2=as.numeric(survival.time.2),
              survival.time.2=ifelse(died & had.sec, survival.time.2, NA))

>>>>

tbl.pre <- data %>%
    transmute(site=CENTER,
              race=race,
              age.ge.40=ifelse(age.at.aids >= 40,
                               "age >= 40", "age < 40"),
              aids.year=cut(year(aids.date), c(1984, 1988, 1992, 1995), 
                                 include.lowest=TRUE, right=FALSE),
              cd4.base=cut(cd4, c(0, 50, 200, Inf), include.lowest=TRUE,
                           right=FALSE),
              initial.aids=frst.aids.diag,
              second.aids=sec.aids.diag,
              depressed=ifelse(depression, "depressed", "not depressed"),
              drug.user=ifelse(drug.use, "Drug User", "Not a Drug User"),
              site=CENTER,
              died=year(death.date) < 2100,
              survival.time=difftime(death.date, aids.date, 
                                     units="weeks") / 52.25 * 12,
              survival.time=as.numeric(survival.time),
              survival.time=ifelse(died, survival.time, NA),
              survival.time.2=difftime(death.date, sec.aids.date,
                                       units="weeks") / 52.25 * 12,
              survival.time.2=as.numeric(survival.time.2),
              survival.time.2=ifelse(died & had.sec, survival.time.2, NA))
